Unrecognized States: A Theory of Self-Determination and Foreign Influence

### 2015-10-16 eqm_profiles.tex
start reasoning about relevant regions of state variables
minor clarifications to eqm_profiles.tex

Strategies
\begin{itemize}
	\item For patron: function of $q_{st}$
	\item For c: function of $q_{st} + R_{pt}$
	\item For s: function of $Q_{st}=q_{st} + R_{pt} + R_{ct}$
	\item For g: not a function of $q_{st}$ at all
\end{itemize}

@@

\vskip.5in
We have six state variables, so $s = \left(q_s,q_g,l_s,l_g,w_s,w_g \right)$.
\begin{itemize}
	\item Strategies are a function of all six state variables
	\item Strategies for the patron and $c$ are also how much to invest in each of the six state variables. Some can be ruled out by preference assumptions:
		\begin{itemize}
			\item $c$ dislikes war, so will never invest in $w_s$ or $w_g$. It would also not want to make the government lose, so won't invest in $l_g$ either.
			\item Because the patron's preferences are aligned with the secessionists and against the government, it never invests in $w_g$ or $l_s$.
		\end{itemize}
\end{itemize}

\vskip.5in
Note that patron will never invest to augment $l_s$ or $w_g$. This leave four state varibles in which the patron may invest: $q_s$, $q_g$, $l_g$ and $w_s$.
\begin{itemize}
	\item Also, Gov't / Secessionists: Choose unilateral, simultaneous best responses depending on magnitudes of $Q_{i1}$, $L_{i1}$ and $\omega_{i1}$
		\begin{itemize}
			\item Game only continues if (SQ,SQ) or (Cede, Cede) was played
		\end{itemize}
\end{itemize}

Period 1
\begin{enumerate}
	\item Patron: $R_{p1} = \frac{\beta}{1-\de} - \left(q_{s1} - l_{s1}\right)$ to augment $q_{s1}$ if this is greater than 0. Else, $R_{p1} = 0$. Can write in max language.
		\begin{itemize}
			\item International community: 
				\begin{enumerate}
					\item If $R_{p1} + q_{s1} - l_{s1} \geq \frac{\beta}{1-\de}$, $R_{c1} =0$
					\item Otherwise $R_{c1} = l_{s1} - \left(q_{s1} + R_{p1} \right) + \ve$ to augment $l_{s1}$
						\begin{itemize}
							\item (SQ,Cede) is played and game ends
						\end{itemize}
				\end{enumerate}
		\end{itemize}	
	\item Patron might also want to invest to encourage recognition directly. How much to augment $l_{g1}$?	
	\item Patron might also want to instigate fighting. If $\frac{\lambda p_{1s} - \alpha (1-p_{1s}) + \mu + \beta}{1 - \de}$ is positive, invest in $w_{s1}$ to change $\omega_{s1}$. Will not invest in $w_{s1}$ when the quantity is non-positive.
		\begin{itemize}
			\item $c$ will counter up to $\frac{\nu p_{1s} - \beta (1-p_{1s})}{1 -\de}$
		\end{itemize}
	\item Patron could also invest in $q_g$ to counter investment by $c$ in government's payoffs. But this would only been needed if $c$ had incentive to invest in $g$ playing Fight, and we've ruled that out.
\end{enumerate}

>>>>

\vskip.2in
Strategies (this is for the most interesting state variable, but could write it out for the other five)
\begin{itemize}
	\item For patron: function of $q_{st}$
	\item For c: function of $q_{st} + R_{pt}$
	\item For s: function of $Q_{st}=q_{st} + R_{pt} + R_{ct}$
	\item For g: not a function of $q_{st}$ at all
\end{itemize}

@@

\vskip.5in
We have six state variables, so $s = \left(q_s,q_g,l_s,l_g,w_s,w_g \right)$.
\begin{itemize}
	\item Strategies are a function of all six state variables
		\begin{itemize}
			\item We can restrict attention to relevant ranges of the state variables. CAN I CHANGE PROP 1 PARTS 1 AND 2 TO BE INITIAL VALUES OF STATE VARIABLES? If so, then these conditions and what is necessary in each period to make the game continue.
		\end{itemize}
	\item Strategies for the patron and $c$ are also how much to invest in each of the six state variables. Some can be ruled out by preference assumptions:
		\begin{itemize}
			\item $c$ dislikes war, so will never invest in $w_s$ or $w_g$. It would also not want to make the government lose, so won't invest in $l_g$ either.
			\item Because the patron's preferences are aligned with the secessionists and against the government, it never invests in $w_g$ or $l_s$.
		\end{itemize}
\end{itemize}

\vskip.5in
This leaves four state varibles in which the patron may invest: $q_s$, $q_g$, $l_g$ and $w_s$. Three in which $c$ may invest: $q_s$, $q_g$, $l_s$.
\begin{itemize}
	\item Also, Gov't / Secessionists: Choose unilateral, simultaneous best responses depending on magnitudes of $Q_{i1}$, $L_{i1}$ and $\omega_{i1}$
		\begin{itemize}
			\item Game only continues if (SQ,SQ) or (Cede, Cede) was played
		\end{itemize}
\end{itemize}

\vskip.2in
Period 1
\begin{enumerate}
	\item Patron: $R_{p1} = \frac{\beta}{1-\de} - \left(q_{s1} - l_{s1}\right)$ to augment $q_{s1}$ if this is greater than 0. Else, $R_{p1} = 0$. Can write in max language.
		\begin{itemize}
			\item International community: 
				\begin{enumerate}
					\item If $R_{p1} + q_{s1} - l_{s1} \geq \frac{\beta}{1-\de}$, $R_{c1} =0$
					\item Otherwise $R_{c1} = l_{s1} - \left(q_{s1} + R_{p1} \right) + \ve$ to augment $l_{s1}$
						\begin{itemize}
							\item (SQ,Cede) is played and game ends
						\end{itemize}
				\end{enumerate}
		\end{itemize}	
	\item Patron might also want to invest to encourage recognition directly. How much to augment $l_{g1}$?	
	\item Patron might also want to instigate fighting. If $\frac{\lambda p_{1s} - \alpha (1-p_{1s}) + \mu + \beta}{1 - \de}$ is positive, invest in $w_{s1}$ to change $\omega_{s1}$. Will not invest in $w_{s1}$ when the quantity is non-positive.
		\begin{itemize}
			\item $c$ will counter up to $\frac{\nu p_{1s} - \beta (1-p_{1s})}{1 -\de}$
		\end{itemize}
	\item Patron could also invest in $q_g$ to counter investment by $c$ in government's payoffs. But this would only been needed if $c$ had incentive to invest in $g$ playing Fight, and we've ruled that out.
\end{enumerate}
